The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-30 paper.tex
update

\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} = \frac{3}{4}\sigma_{T}c\textit{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
               \gamma^{-(p+2)}f(q, \Gamma)d\gamma.
\end{equation}

\begin{equation}
f(\gamma_{\text{e}}, \epsilon) = 2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},
\end{equation}

\begin{equation}
\Gamma=\frac{4\epsilon \gamma_{\text{e}}}{m_{\text{e}}c^2}
\end{equation}

@@

\begin{equation}
q=\frac{\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}\right)}.
\end{equation}

>>>>

In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The emissivity of the upscattered photons at the energy $\epsilon_{1}$ is given by\
\citet{Jones1968,BLUMENTHAL1970}.

\begin{subequations}
  \begin{align}
  &\frac{dE}{dtd\epsilon_{1}dV} =\nonumber\\
               &\frac{3}{4}\sigma_{T}c\textit{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
               \gamma^{-(p+2)}f(q, \Gamma)d\gamma,\\
  \nonumber\\
  &f(q, \Gamma) =\nonumber\\
               &2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},\\
  &q=\frac{\epsilon_{1}/\gamma_{\text{e}}\
               m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}\right)},\\
  &\Gamma=\frac{4\epsilon \gamma_{\text{e}}}{m_{\text{e}}c^2},
  \end{align}
\end{subequations}

where $\gamma_{\text{min}}(\epsilon)$ and $\gamma_{\text{max}}=10^{6}$\
are the minimum and maximum Lorentz factor of CRe,\
$n(\epsilon)$ is the photon number density of ISRF per energy,

We set $\gamma_{\text{max}}$ to be $10^{6}$, corresponding to the cutoff CRe energy $0.5$ GeV,\
$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe such that CRe is energetic enough to\
produce scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.

@@

\begin{equation}
\gamma_{\text{min}}=\
 0.5\left(\frac{\epsilon_{1}}{mc^2}+\sqrt{\left(\frac{\epsilon_{1}}{mc^2}\right)^2+\
 \frac{\epsilon_{1}}{\epsilon}}\right).
\end{equation}
